Consistency scores in text data

### 2020-07-29 outputs/documents/paper.Rmd
Updated write-ups and added more literatures

## Word Embedding Models
Moved from statistical to neural network. Word embedding models works by representing words as numerical dense vectors so the neural networks can understand and process. Representing words as dense vectors has a long history, but the first neural network language model was proposed in 2013 by @bengio2003neural, and became the pioneer in word embedding models. In the work of @bengio2003neural, word embedding works by encoding the words into a feature vector. The feature vector represents different aspects of the word and each word is associated with a point in a vector space.

>>>>

## Word Embedding Models
[Moved from statistical to neural network] Word embedding models works by representing words as numerical dense vectors so the neural networks can understand and process. Representing words as dense vectors has a long history, but the first neural network language model was proposed in 2013 by @bengio2003neural, and became the pioneer in word embedding models. In the work of @bengio2003neural, word embedding works by encoding the words into a feature vector. The feature vector represents different aspects of the word and each word is associated with a point in a vector space.
